\begin{longtblr}[
  caption = {UC 1.3: Exit Parking for Learners/Faculty Members},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 1.3 \\
Use Case Name & Exit Parking for Learners/Faculty Members \\
Actors & Primary: Learners, Faculty Members \& Staff. \par Supporting: Gateway, HCMUT\_SSO. \\
Description & The exit process for registered members. The system verifies their entry session. \\
Pre-conditions & The user has an active parking session inside the campus. \\
Post-conditions & The parking session is marked as completed. The fee is calculated and added to their billing cycle. \\
Main Flow & 
1. The user drives to the exit gate and taps their official ID card. \par
2. The camera captures the license plate. \par
3. The system retrieves the active parking session associated with the card and verifies that the captured plate matches the entry plate. \par
4. The system calculates the fee (role-based pricing policy). \par
5. The system accumulates this fee into the user's current billing cycle (to be processed via BKPAY at the end of the month/cycle). \par
6. The system closes the session and opens the barrier. \par
7. The barrier closes after the vehicle passes. \\
Exception Flows & 
\textbf{E1: Lost ID Card inside the Campus:} If the member lost their ID card, the flow transfers to UC 1.7 (Main User Card Lost). The operator supports the member, invalidates the lost card, issues a replacement, and clears the session. \par \vspace{0.5em}
\textbf{E2: Plate Mismatch or Barrier Stuck:} If the exit camera detects a mismatch or if the barrier malfunctions, the flow transfers to UC 1.5 (Manual Controlling) for manual verification. \par \vspace{0.5em}
\textbf{E3: Unpaid Previous Debt:} The system detects an unpaid BKPAY bill. The barrier remains closed, prompting the user to settle their account. \\
\end{longtblr}