\begin{longtblr}[
  caption = {UC 1.1. Enter Parking for Learners/Faculty Members},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, % Cột 1 rộng 3.5cm, Cột 2 rộng 11cm, căn lề trái
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, % Dòng đầu tiên có nền xám và chữ đậm
  rowhead = 0, % Không lặp lại header ở trang sau theo yêu cầu của bạn
}
Field & Details \\
Use Case ID & 1.1 \\
Use Case Name & Enter Parking for Learners/Faculty Members \\
Actors & Primary: Learners, Faculty Members \& Staff. \par Supporting: Gateway, Camera, Sensors, HCMUT\_SSO. \\
Description & The automatic entry process for university members who possess a registered official ID card integrated with the SSO system. \\
Pre-conditions & The entry hardware is online. The barrier is closed. \\
Post-conditions & A new parking session is recorded. The barrier opens. \\
Main Flow & 
1. The user drives to the entry gate and taps their official ID card on the reader. \par
2. The camera captures the vehicle's license plate. \par
3. The system sends the card data to HCMUT\_SSO for authentication. \par
4. Upon valid authentication, the system checks if the user's account is active and has no parking ban. \par
5. The system creates a new ``Member Parking Session'' containing the timestamp, card ID, and license plate. \par
6. The system opens the barrier. \par
7. Once the vehicle passes the loop detector, the barrier closes. \\
Alternate Flows & 
\textbf{E1: Parking Lot is Full:} If the system detects that the parking area has reached maximum capacity, the flow is transferred to UC 1.8 (Handle Parking Full State). The system will close the gateway and notify participants. The card tap is rejected. \par \vspace{0.5em}
\textbf{E2: Sensor/Camera Error or Unrecognized Plate:} If the hardware fails to read the license plate or the automatic flow is interrupted, the system alerts the Parking Operator. The flow transfers to UC 1.5 (Manual Controlling). \par \vspace{0.5em}
\textbf{E3: Forgot/Lost ID Card at Entry Gate:} If a member arrives without a card, the user presses the button on the card dispenser to take a temporary card. The process immediately transfers to UC 1.2 (Enter Parking for Temporary Visitors). \par \vspace{0.5em}
\textbf{E4: Invalid/Inactive Card:} The SSO system returns an invalid status (e.g., account suspended, unpaid fees). The barrier remains closed, and an error message is displayed. The user can opt to take a temporary card (transfer to UC 1.2). \\
\end{longtblr}