\begin{longtblr}[
  caption = {UC 3.5: View Overall Finance Report},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 3.5 \\
Use Case Name & View Overall Finance Report \\
Actors & Primary: HCMUT Finance Office, HCMUT Leaders \& Managers. \par Supporting: None. \\
Description & This use case allows authorized financial staff and university management to view, analyze, and export aggregated financial data from the smart parking system through strategic dashboards and detailed reports. \\
Trigger & The user navigates to the ``Financial Reports'' or ``Management Dashboard'' module on the web application. \\
Pre-conditions & 1. The user has successfully authenticated and logged in via HCMUT\_SSO. \par 2. The user's role is strictly verified via RBAC as either ``Finance Admin'' or ``University Management.'' \\
Post-conditions & The system successfully presents the aggregated financial data without modifying any underlying transaction records (Read-only operation). \\
Main Flow & 
1. The user selects the ``Financial Reports'' module from the navigation menu. \par
2. The system queries the database to aggregate revenue data across all parking sessions and payment methods (BKPAY periodic, BKPAY dynamic QR, and Cash). \par
3. The system displays a high-level strategic dashboard including: Total revenue, revenue breakdown by user categories, and visual charts showing trends over time. \par
4. The user applies data filters to adjust the strategic view (e.g., selecting a specific quarter, year, or a specific parking zone). \par
5. The system dynamically updates the dashboard metrics and charts based on the applied filters. \par
6. The user clicks the ``Export Financial Report'' button to download the data. \par
7. The system generates a formal report (PDF or Excel) containing both the high-level summary and detailed transaction logs. \par
8. The system initiates the file download to the user's device. \\
Alternate Flows & 
\textbf{A1 - No Financial Data for Selected Period:} At step 5, if no transactions match the selected filters, the system displays empty charts and a message: ``No financial data available for the selected period.'' \\
Exception Flows & 
\textbf{E1 - Data Retrieval Timeout (Large Data Volume):} At step 2 or 5, if a query causes a timeout, the system safely aborts the process and displays: ``The requested report is too large and timed out. Please select a narrower time range (e.g., up to 6 months) and try again.'' \\
\end{longtblr}