\begin{longtblr}[
  caption = {UC 1.7: Main User Card Lost},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 1.7 \\
Use Case Name & Main User Card Lost \\
Actors & Primary: Parking Operators. \par Supporting: Learners, Faculty Members \& Staff. \\
Description & Manages the situation where a university member loses their official ID card while parked inside the campus. The operator assists in verifying their identity, invalidating the old card, and clearing the session. \\
Pre-conditions & A member arrives at the exit without their ID card. The flow is transferred from UC 1.3. \\
Post-conditions & The lost ID card is deactivated in the parking system, the fee is linked to BKPAY, and the user is allowed to exit. \\
Main Flow & 
1. The university member notifies the Parking Operator that they lost their ID card inside the campus. \par
2. The Operator looks up the member's active parking session using their vehicle's license plate or their student/staff ID number. \par
3. The Operator verifies the member's identity against the system data (read-only data synced from HCMUT\_DATACORE, such as checking their profile picture). \par
4. The system calculates the parking fee and adds it to the user's BKPAY billing cycle as usual. \par
5. The Operator marks the lost ID card as ``Invalid/Lost'' in the system to prevent unauthorized access if someone else finds it. \par
6. The system closes the active parking session. \par
7. The Operator manually triggers the barrier to let the member exit. \\
Exception Flows & 
\textbf{E1: Identity Verification Fails:} The driver does not match the profile picture or information associated with the student/staff ID in the system. The Operator refuses exit and contacts campus security for suspected vehicle theft. \\
\end{longtblr}