\begin{longtblr}[
  caption = {UC 1.2: Enter Parking for Temporary Visitors},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 1.2 \\
Use Case Name & Enter Parking for Temporary Visitors \\
Actors & Primary: Temporary Visitors.\par Supporting: Gateway, Camera, Sensors. \\
Description & The entry process for guests who do not have a university ID, using a temporary card mechanism independent of the centralized SSO. \\
Pre-conditions & The card dispenser is functional and stocked with cards. \\
Post-conditions & An independent guest session is created. The barrier opens. \\
Main Flow & 
1. The visitor drives to the entry gate and presses the button on the card dispenser. \par
2. The dispenser issues a temporary parking card. \par
3. The camera captures the vehicle's license plate. \par
4. The system creates a new ``Guest Parking Session'' linked to the temporary card ID and the captured plate. \par
5. The system opens the barrier. \par
6. The barrier closes after the vehicle passes. \\
Alternate Flows & 
\textbf{E1: Parking Lot is Full:} The system transfers to UC 1.8 (Handle Parking Full State). The card dispenser is disabled, preventing new cards from being issued. \par \vspace{0.5em}
\textbf{E2: Dispenser Empty or Hardware Failure:} If the card machine runs out of cards or malfunctions, the flow transfers to UC 1.5 (Manual Controlling) for the Parking Operator to manually process the entry. \\
\end{longtblr}