\begin{longtblr}[
  caption = {UC 3.1: Pay periodic parking fee},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 3.1 \\
Use Case Name & Pay periodic parking fee \\
Actors & Primary: Learners, Faculty Members \& Staff. \par Supporting: BKPAY. \\
Description & This use case allows registered users to pay their periodic parking fees via the BKPAY system using a linked OCB account or a dynamic QR code. \\
Trigger & The user navigates to the ``Billing \& Payment'' section on the web app and clicks ``Pay Fee.'' \\
Pre-conditions & 1. User is authenticated via HCMUT\_SSO. \par 2. Profile is synchronized from HCMUT\_DATACORE. \par 3. Outstanding fee is calculated based on institutional pricing policy. \\
Post-conditions & 1. Fee is successfully paid and balance is cleared. \par 2. Transaction is saved in the Billing History. \\
Main Flow & 
1. The user accesses the ``Billing \& Payment'' module. \par
2. The system retrieves and displays the current outstanding periodic parking fee. \par
3. The user selects the fee and clicks ``Pay Now.'' \par
4. The system initiates the request and redirects the user to BKPAY. \par
5. BKPAY displays options: Sub-flow A (OCB) or Sub-flow B (QR Code). \par
6. BKPAY sends a success confirmation back to the parking system. \par
7. The system updates the fee status to ``Paid'' and clears the balance. \par
8. The system saves transaction details and redirects to a success page. \\
Sub-flows & 
\textbf{Sub-flow A: Linked OCB account} \par
The user selects OCB method. BKPAY displays fee details. The user confirms, and the system automatically deducts the amount from the linked account. \par \vspace{0.5em}
\textbf{Sub-flow B: Dynamic QR Code} \par
The user selects QR method. BKPAY generates a VietQR code. The user scans via banking app and authorizes the transfer. BKPAY receives the notification. \\
Alternate Flows & 
\textbf{A1 - User cancels payment:} At step 5, the user chooses to cancel. BKPAY redirects back with a ``Cancelled'' status. The system displays a cancellation message and the fee remains unpaid. \\
Exception Flows & 
\textbf{E1 - Payment failed/Declined:} BKPAY declines the transaction (insufficient funds, wrong OTP). The system displays: ``Payment failed. Please check details or try another method.'' \par \vspace{0.5em}
\textbf{E2 - BKPAY Gateway Timeout:} The system fails to connect to BKPAY. The system logs the error and displays: ``Payment gateway is currently unavailable. Please try again later.'' \\
\end{longtblr}