\begin{longtblr}[
  caption = {UC 3.2: Pay temporary visitor fee},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 3.2 \\
Use Case Name & Pay temporary visitor fee \\
Actors & Primary: Temporary Visitors. \par Supporting: Parking Operators, BKPAY (Payment Gateway). \\
Description & This use case allows temporary visitors to pay their parking fees when exiting the campus via a dynamic BKPAY QR code or cash. \\
Trigger & The Temporary Visitor arrives at the exit gate and presents their temporary parking card. \\
Pre-conditions & 1. Valid ongoing parking session exists. \par 2. Visitor is physically present at the exit gate. \par 3. Fee is calculated based on duration and visitor pricing policy. \\
Post-conditions & 1. Fee is successfully paid and session is closed. \par 2. Transaction is saved in the database. \par 3. Exit barrier opens (Triggers UC 1.4). \\
Main Flow & 
1. The Temporary Visitor presents the temporary parking card at the exit gate. \par
2. The Parking Operator scans the card (or the visitor scans it at the automated terminal). \par
3. The system retrieves the session, calculates the fee, and displays the total amount. \par
4. The visitor selects a payment method: Sub-flow A (QR Code) or Sub-flow B (Cash). \par
5. Upon successful payment, the system updates the status to ``Paid''. \par
6. The system saves the transaction details into the database. \par
7. The system displays a success message and triggers the barrier to open. \\
Sub-flows & 
\textbf{Sub-flow A: Pay via Dynamic QR Code (BKPAY)} \par
The visitor chooses bank transfer. The system displays a dynamic VietQR code. The visitor scans via a mobile banking app and authorizes the transfer. BKPAY sends a confirmation to the parking system. \par \vspace{0.5em}
\textbf{Sub-flow B: Pay via Cash} \par
The visitor hands cash to the Parking Operator. The Operator returns change if necessary and manually confirms the receipt by clicking ``Confirm Cash Payment'' on the system interface. \\
Alternate Flows & 
\textbf{A1 - Change Payment Method:} At step 4, the visitor decides to switch methods (e.g., from QR to Cash). The Operator cancels the QR generation and selects the Cash option, proceeding to Sub-flow B. \\
Exception Flows & 
\textbf{E1 - Card Lost/Unreadable:} The system cannot automatically calculate the fee. The flow transfers to UC 1.6 (Handle temporary card lost) for manual penalty processing. \par \vspace{0.5em}
\textbf{E2 - BKPAY Webhook Delay/Network Issue:} If the transfer is successful on the visitor's phone but the system doesn't receive the webhook, the Operator visually verifies the transaction and uses the ``Manually Override - Force Paid'' function with a recorded note. \\
\end{longtblr}