\begin{longtblr}[
  caption = {UC 1.6: Temporary Card Lost},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 1.6 \\
Use Case Name & Temporary Card Lost \\
Actors & Primary: Parking Operators. \par Supporting: Temporary Visitors. \\
Description & Handles the scenario where a temporary visitor loses their parking card before exiting. The system calculates the fee and invalidates the lost card to prevent unauthorized use. \\
Pre-conditions & The visitor arrives at the exit gate without their temporary card. The flow is transferred from UC 1.4. \\
Post-conditions & The lost card is temporarily invalidated, the penalty/parking fee is collected, and the guest session is closed. \\
Main Flow & 
1. The Temporary Visitor informs the Parking Operator about the lost card. \par
2. The Operator uses the system's search function, entering the vehicle's license plate captured by the exit camera. \par
3. The system retrieves the original ``Guest Parking Session'' matching the license plate and displays the entry time. \par
4. The Operator verifies the vehicle and driver identity. \par
5. The system calculates the standard parking fee based on duration, plus an automatic ``Lost card Surcharge.'' \par
6. The Operator collects the total fee via cash or QR code. \par
7. The system temporarily marks the lost temporary card ID as ``Invalid'' to prevent it from being used by someone else later. \par
8. The system closes the session and triggers the barrier to open for exit. \\
Exception Flows & 
\textbf{E1: License Plate Not Found:} The system cannot find an entry record matching the license plate. The Operator must manually search the database by estimated entry time or vehicle description to locate the session. \\
\end{longtblr}