\begin{longtblr}[
  caption = {UC 3.7: Reconcile Financial Data},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 3.7 \\
Use Case Name & Reconcile Financial Data \\
Actors & Primary: HCMUT Finance Office. \par Supporting: BKPAY. \\
Description & This use case allows the Finance Office to cross-check records in the Smart Parking System against BKPAY settlement data to identify and resolve financial discrepancies. \\
Trigger & The Finance Officer initiates a manual sync via the ``Reconciliation'' module, or the system triggers an automated background reconciliation. \\
Pre-conditions & 1. User is authenticated via HCMUT\_SSO. \par 2. User possesses the ``Finance Admin'' role. \par 3. BKPAY APIs or settlement files are accessible. \\
Post-conditions & 1. Discrepancies are identified and resolved. \par 2. Relevant support tickets from UC 3.6 are updated. \par 3. Reconciliation report is logged in the Audit Trail. \\
Main Flow & 
1. The user accesses the ``Reconciliation'' module on the web application. \par
2. The user selects a date range and clicks ``Run Reconciliation.'' \par
3. The system retrieves all local parking transaction records for the period. \par
4. The system calls the BKPAY API (or parses an uploaded file) to fetch actual payment logs. \par
5. The system performs an automated cross-match based on Transaction IDs and amounts. \par
6. The system displays a Dashboard with three tabs: Matched, Discrepancies, and Pending Tickets. \par
7. The user reviews a mismatched transaction in the ``Discrepancies'' tab. \par
8. The system highlights the difference (e.g., Local = Unpaid, BKPAY = Paid). \par
9. The user clicks ``Force Sync - Mark as Paid.'' \par
10. The system updates the local status to ``Paid,'' clears debt, and logs the manual override. \par
11. If linked to a UC 3.6 ticket, the system marks it as ``Resolved'' and notifies the user. \\
Alternate Flows & 
\textbf{A1 - 100\% Match (No Discrepancies):} If all records match, the system displays a ``Perfect Match'' green banner. The user clicks ``Approve \& Close Cycle.'' \par \vspace{0.5em}
\textbf{A2 - Initiate Refund:} If an overcharge is detected, the Finance Officer clicks ``Initiate Refund.'' The system sends a request to BKPAY and sets the status to ``Refund Pending.'' \\
Exception Flows & 
\textbf{E1 - BKPAY API Connection Failure:} The system fails to connect or the API key is expired. The system halts the process and displays: ``Unable to connect to BKPAY settlement server. Please check configuration or upload a manual file.'' \par \vspace{0.5em}
\end{longtblr}