\begin{longtblr}[
  caption = {UC 4.1: Authenticate on WEB},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 4.1 \\
Use Case Name & Authenticate on WEB \\
Actors & Primary: Learners, Faculty Members \& Staff. \par Supporting: HCMUT\_SSO. \\
Description & User’s credentials authentication process at the WEB app using the university's centralized Single Sign-On system. \\
Trigger & User navigates to the login page or attempts to access restricted dashboard features. \\
Pre-conditions & User is at the authentication page. \\
Post-conditions & System connects with HCMUT\_SSO to authenticate. Valid credentials grant access; otherwise, the request is rejected. \\
Main Flow & 
1. User navigates to the authentication page. \par
2. User inputs credentials information (Username and Password) into the page. \par
3. The system initiates the authentication process by checking the information with fetched data from HCMUT\_SSO. \par
4. If information is valid, the system provides the user entrance and redirects to the dashboard. \par
5. If information is NOT valid, the system rejects the request and prompts the user to re-input credentials (back to step 2). \\
Exception Flows & 
\textbf{E1 - Connection to Authentication Module/Host Lost:} The system displays a failsafe page indicating a lost connection to the pipeline or host. The user must refresh the page to check status. \par \vspace{0.5em}
\textbf{E2 - Connection to HCMUT\_SSO Lost:} The system displays a failsafe page indicating that the SSO service is unreachable. Access is temporarily restricted until the connection is restored. \\
\end{longtblr}