\begin{longtblr}[
  caption = {UC 4.4: Audit system logs},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 4.4 \\
Use Case Name & Audit system logs \\
Actors & Primary: System Admin, IT Team. \\
Description & Oversight of activity loggings and system logging to ensure transparency and track operational/technical issues. \\
Pre-conditions & Actor passes authentication check (UC 4.1). \\
Post-conditions & Actor gains oversight over reports and loggings of system and onsite activities. \\
Main Flow & 
1. After passing authentication, the actor navigates to the system log sector. \par
2. The system fetches logs from the central database and displays them in categorized lists: \par
\hspace{1em} - \textbf{System Log:} Records of system events and operations. \par
\hspace{1em} - \textbf{Fee Policy Log:} Tracks changes to parking fee rules and privileges. \par
\hspace{1em} - \textbf{Onsite Activity Log:} Captures physical parking activities. \par
\hspace{1em} - \textbf{Onsite Error Report:} Logs errors occurring at the physical infrastructure level. \par
\hspace{1em} - \textbf{System Error Report:} Captures backend/software failures. \par
3. The actor may search for specific entries using keys (Name, ID, Time, Keywords). \par
4. The actor may filter through the lists using the filter feature to narrow down results. \\
Alternate Flows & None. \\
Exception Flows & 
\textbf{E1 - Connection to Authentication/Host Lost:} Displays a failsafe page. The actor must refresh to check the connection status. \par \vspace{0.5em}
\textbf{E2 - Connection to Central Database Lost:} Displays a connection lost message and returns empty lists for the affected categories. \\
\end{longtblr}