\begin{longtblr}[
  caption = {UC 2.2: View and manage parking availability},
]{
  colspec = {Q[l, 3.5cm] Q[l, 11cm]}, 
  hlines, vlines,
  row{1} = {bg=gray9, font=\bfseries}, 
  rowhead = 0, 
}
Field & Details \\
Use Case ID & 2.2 \\
Use Case Name & View and manage parking availability \\
Actors & Primary: Parking Operators. \par Supporting actors: Gateways, Sensors, Signages. \\
Description & Monitor security, coordinate the parking lot, and inspect detailed slot data (time in/out, duration) and specific errors. \\
Trigger & Parking operator accesses the monitor or an error occurs. \\
Pre-conditions & 1. The parking operator is authenticated via UC 4.1. \par 2. The system has an active connection to the IoT network. \\
Post-conditions & 1. Operators maintain the facility. \par 2. Any detected errors are flagged for maintenance. \\
Main Flow & 
1. The Parking Operators are successfully logged into the Web Management System. \par
2. The operator accesses the ``Real-time Occupancy Map'' on the Web App. \par
3. The system retrieves data via connections with sensors, signages and gateway to display real-time slot maps and individual slot details. \par
4. The operator selects a specific slot to view detailed metadata (e.g., Plate ID, Entry Time, Current Duration). \par
5. The operator monitors high-traffic zones to coordinate manual guidance if necessary. \\
Alternate Flows & 
\textbf{A1: Search with filter for specific data (at step 4):} The operator uses the filter tool to view only overstayed vehicles (e.g., cars parked >24 hours). The system highlights the filtered slots on the map, and the operator exports the list for security verification. \\
Exception Flows & 
\textbf{A1: Sensors disconnection (at step 3):} The system detects lost connection or timeout from a specific IoT device. The status is updated to ``OFFLINE/UNKNOWN''. The system and/or Operators notify the IT team and System Admin. The system generates a maintenance ticket in the Error log. \\
\end{longtblr}